---
title: "QC - PART TWO"
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes: "\\usepackage[export]{adjustbox}\n\\let\\includegraphicsbak\\includegraphics\n\\renewcommand*{\\includegraphics}[2][]{\\includegraphicsbak[frame,#1]{#2}}
  \n"
---

# Bisulfite conversion

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Bisulfite_histogram.pdf"))
```

# Methylation vs Unmethylation signal

### Average intensity with threshold 10.5

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/MinfiIntensity_10.5.pdf"))

```


# Raw Beta and M-value distributions

```{r, out.width="650px", out.height="500px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_raw.pdf"))
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Mvalue_distribution_raw.pdf"))
```

# Filtered Beta and M-value distribution

### Autosomal probes

```{r, out.width="650px", out.height="500px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_filtered_1e16.pdf"))
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Mvalue_distribution_filtered_1e16.pdf"))

```

### X-chromosomes of Females

```{r, out.width="650px", out.height="500px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_filtered_1e16_X_females.pdf"))
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Mvalue_distribution_filtered_1e16_X_females.pdf"))

```

### XY-chromosomes of Males

```{r, out.width="650px", out.height="500px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_filtered_1e16_XY_males.pdf"))
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Mvalue_distribution_filtered_1e16_XY_males.pdf"))

```

# Filtered Beta distribution 0BP snps probes

### Autosomal probes

```{r, out.width="650px", out.height="500px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_filtered_1e16_SNP0bp.pdf"))

```

# Filtered Outlier Check

### Autosomal probes

```{r, out.width="650px", out.height="400px", message=FALSE, echo=FALSE}

knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Filtered_beta_outlier_check.pdf"))

```

### X chr probes - Females

```{r, out.width="650px", out.height="400px", message=FALSE, echo=FALSE}

knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Filtered_beta_outlier_check_X_females.pdf"))

```

### XY chr probes - Males

```{r, out.width="650px", out.height="400px", message=FALSE, echo=FALSE}

knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Filtered_beta_outlier_check_XY_males.pdf"))
```

